---
title: "Understanding the customer"
author: "Kahiga Ndegwa"
date: "19/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### 1. Problem Definition
As a data scientist i have been tasked by "Kira Plastinina" which is a youth clothing online store, to use the data available and help the brand’s Sales and Marketing team to understand their customer’s behavior and characteristics of customer groups.
## Metric of Success
1. Perform EDA
2. Perform clustering stating insights drawn from your analysis and visualizations.
3. implementation using K-Means clustering vs Hierarchical clustering highlighting the strengths and limitations of each approach in the context of your analysis. 
```{r}
install.packages('tidyverse')
library(tidyverse)

install.packages('ggplot2')
library(ggplot2)

install.packages('caret')
library(caret)

install.packages('caretEnsemble')
library(caretEnsemble)

install.packages('psych')
library(psych)

install.packages('Amelia')
library(Amelia)

install.packages('mice')
library(mice)

install.packages('GGally')
library(GGally)

install.packages('rpart')
library(rpart)

install.packages('randomForest')
library(randomForest)
```

###2. Data Sourcing
The data we used was collected by the firm for the past one year
###3Loading The data
```{r}
data <- read.csv("C:/Users/user/Desktop/online_shoppers_intention.csv")
```
###3.Check the Data

```{r}
# Looking at the structure of our data
# ---
# 
str(data)
```
```{r}
# Previewing our data
head(data)
```

```{R}
# Understanding our dataset
# ---
# 
describe(data)
```

```{r}
# We visualize our dataset by checking how many missing values
# ---
# 
missmap(data)

```


##Perform Data Cleaning
##Perform Exploratory Data Analysis  (Univariate, Bivariate & Multivariate)
##Implement the Solution
##Challenge the Solution
##Follow up Questions