---
title: "Understanding the customer"
author: "Kahiga Ndegwa"
date: "19/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### 1. Problem Definition
As a data scientist i have been tasked by "Kira Plastinina" which is a youth clothing online store, to use the data available and help the brand’s Sales and Marketing team to understand their customer’s behavior and characteristics of customer groups.
## Metric of Success
1. Perform EDA
2. Perform clustering stating insights drawn from your analysis and visualizations.
3. implementation using K-Means clustering vs Hierarchical clustering highlighting the strengths and limitations of each approach in the context of your analysis. 
```{r}
install.packages('tidyverse')
library(tidyverse)

install.packages('ggplot2')
library(ggplot2)

install.packages('caret')
library(caret)

install.packages('caretEnsemble')
library(caretEnsemble)

install.packages('psych')
library(psych)

install.packages('Amelia')
library(Amelia)

install.packages('mice')
library(mice)

install.packages('GGally')
library(GGally)

install.packages('rpart')
library(rpart)

install.packages('randomForest')
library(randomForest)
```

###2. Data Sourcing
The data we used was collected by the firm for the past one year
###3Loading The data
```{r}
data <- read.csv("C:/Users/user/Desktop/online_shoppers_intention.csv")
```
###3.Check the Data

```{r}
# Looking at the structure of our data
# ---
# 
str(data)
```
```{r}
# Previewing our data
head(data)
```

```{R}
# Understanding our dataset
# ---
# 
library(Hmisc)
describe(data)
```
```{r}
unique(data)
```

##Perform Data Cleaning
```{r}
sum(is.na(data))
```
```{r}
na.omit(data)
```
# We visualize our dataset by checking how many missing values
```{r}

# ---
# 
library(Amelia)
missmap(data)

```

```{r}
sum(duplicated(data))
```
```{r}
#Remove duplicated rows based on all rows
data %>% distinct(Administrative,
Administrative_Duration,Informational,Informational_Duration,ProductRelated,ProductRelated_Duration,BounceRates,ExitRates,PageValues,SpecialDay,Month,OperatingSystems,Browser,Region,TrafficType,VisitorType,Weekend,Revenue, .keep_all = TRUE)
```
##Perform Exploratory Data Analysis  (Univariate, Bivariate & Multivariate)
#Univariate Analysis
```{r}
qplot(data$Month, geom = "bar")
```
```{r}
pie(table(data$Weekend), main="weekends")
```
```{r}
qplot(data$Region, geom = "bar")
```
```{r}
qplot(data$SpecialDay, geom = "bar")
```
##Bivariate Analysis
```{r}
barplot(height= data$Informational, names.arg = data$Region)
```
```{r}
library(ggplot2)
qplot(x = data$ProductRelated, y = data$ProductRelated_Duration)
```

```{r}
plot(data[, 1:3])
```

```{r}
plot(data[, 4:6])
```

```{r}
plot(data[, 7:10])
```
```{r}
scatterplot3d(data[1:2])
```

line graph
```{r}
plot(x = data$Browser, y = data$Region, type = "l")
```

```{r}
# boxplot of mpg by cyl
boxplot(Browser ~ Region, data = data)
```

#heatmap(mydata)
```{r}
#highlighting numeric columns
mydata <- data[, c(1,2,3,4,5,6,7,8,9,10)]
head(mydata)
cormat <- round(cor(mydata),2)
head(cormat)

library(reshape2)
melted_cormat <- melt(cormat)
head(melted_cormat)

library(ggplot2)
ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()
```

#1. May,march,Dev and november are the most visited website months
#2. week correlation between all the columns
#3. most people visited the website on Weekdays
#4. Region assigned 0 Aand Special day assigned 0 are the leading areas and days
#5. Information collected at region 3 was the most
#6. from the pairplots most columns are linear and positively skewwed

##Multivariate Analysis
```{r}
library(RColorBrewer)

names <- c("Administrative",
"Administrative_Duration","Informational","Informational_Duration","ProductRelated","ProductRelated_Duration","BounceRates","ExitRates","PageValues")
mylist <- list(data$Administrative,
data$Administrative_Duration,data$Informational,data$Informational_Duration,data$ProductRelated,data$ProductRelated_Duration,data$BounceRates,data$ExitRates,data$PageValues)
makeProfilePlot(mylist,names)
```
```{r}
mosthighlycorrelated <- function(mydataframe,numtoreport)
  {
     # find the correlations
     cormatrix <- cor(mydataframe)
     # set the correlations on the diagonal or lower triangle to zero,
     # so they will not be reported as the highest ones:
     diag(cormatrix) <- 0
     cormatrix[lower.tri(cormatrix)] <- 0
     # flatten the matrix into a dataframe for easy sorting
     fm <- as.data.frame(as.table(cormatrix))
     # assign human-friendly names
     names(fm) <- c("First.Variable", "Second.Variable","Correlation")
     # sort and print the top n correlations
     head(fm[order(abs(fm$Correlation),decreasing=T),],n=numtoreport)
}
```
```{r}
mosthighlycorrelated(data[1:10], 10)
```
```{r}
data[sapply(data, is.numeric)] <- lapply(data[sapply(data, is.numeric)], function(x) ifelse(is.na(x), mean(x, na.rm = TRUE), x))
```
```{r}
standardisedconcentrations <- as.data.frame(scale(data[1:10]))
sapply(standardisedconcentrations,mean)
```
```{r}
standardisedconcentrations <- as.data.frame(scale(data[1:10]))
# standardise the variables
data.pca <- prcomp(standardisedconcentrations)  
```
```{r}
summary(data.pca)
```
```{r}
data.pca$sdev
```
#Deciding how many pcas to retain
```{r}
screeplot(data.pca, type="lines")
```
#from out multivariate analysis at variance 3 is elbowed
#the variance increases as we more pca is don

##Implement the Solution
#K-Means clustering

```{r}
data.new<- data[, c(1, 2, 4,5,6,7,8,9,10,11,12,13,14,15,16,17,18)]
data.class <- data[, "Informational"]
head(data.new)
```
```{r}
normalize <- function(x){
  return ((x-min(x)) / (max(x)-min(x)))
}

data.new$data.Administrative<- normalize(data.new$Administrative)
data.new$data.Administrative_Duration<- normalize(data.new$Administrative_Duration)
data.new$data.Informational<- normalize(data.new$Informational)
data.new$data.Informational_Duration<- normalize(data.new$Informational_Duration)
data.new$data.ProductRelated<- normalize(data.new$ProductRelated)
data.new$data.ProductRelated_Duration<- normalize(data.new$ProductRelated_Duration)
data.new$data.BounceRates<- normalize(data.new$BounceRates)
data.new$data.ExitRates<- normalize(data.new$ExitRates)
data.new$data.PageValues<- normalize(data.new$PageValues)
data.new$data.SpecialDay<- normalize(data.new$SpecialDay)
data.new$data.OperatingSystems<- normalize(data.new$OperatingSystems)
data.new$data.Browser<- normalize(data.new$Browser)
data.new$data.Region<- normalize(data.new$Region)
data.new$data.Weekend<- normalize(data.new$Weekend)
data.new$data.Revenue<- normalize(data.new$Revenue)
head(data.new)
```
```{r}
# Applying the K-means clustering algorithm with no. of centroids(k)=3
# ---
# 
results <- kmeans(na.omit(data.class),3) # this helps in omitting NA 
results
```
```{R}
# Getting the value of cluster center datapoint value(3 centers for k=3)
# ---
# 
results$centers 
```
```{r}
results$cluster
```
```{r}
par(mfrow = c(1,2), mar = c(5,4,2,2))
plot(data.new[,1:5], col = results$cluster) 
```
```{r}
plot(data.new[c(1,4)], col = data.class)
```
```{r}
plot(data.new[c(1,2)], col = results$cluster)
par(mfrow = c(2,2), mar = c(5,4,2,2))
plot(data.new[c(3,4)], col = results$cluster)
plot(data.new[c(3,4)], col = data.class)

```
```{r}
table(results$cluster, data.class)
```
##Challenge the Solution
#Hierarchical clustering
```{r}
x <- rbind(matrix(rnorm(100, sd = 0.3), ncol = 2),
           matrix(rnorm(100, mean = 1, sd = 0.3), ncol = 2))
colnames(x) <- c("x","y")
summary(x)
```
```{r}
summary(data)
```
```{r}
data <- dist(data[,1:4])
hcluster <- hclust(data)
hcluster
```
```{r}
hcd <- as.dendrogram(hcluster)
nodePar <- list(lab.cex = 0.6, pch = c(20,19),
                cex = 0.7, col = c("green","yellow"))
plot(hcd, xlab = "Height", nodePar = nodePar, main = "Cluster dendrogram",
     edgePar = list(col = c("red","blue"), lwd = 2:1), horiz = TRUE )
```
##Follow up Questions
Do I have the right information?
yes